---
title: "Tuning Parameter Selection"
header-includes:
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
```

## Two important elements 

1. Size of $\lambda_{min} = \lambda_{max} \cdot \varepsilon$
2. Size of threshold ($\gamma$) where
\[k = \sup\left\{k \mid dr_k > \gamma \cdot \max_{q} dr_q,\  k \in K \right\}\]

## Found Possible issues

1. I have used $\varepsilon=0.05$, but it tends to estimate too many edges.
2. I also have used $\gamma=0.3$, and it still provides a lot of edges, consequently, bad evaluation results.


## Check up many possible cases 

1. Simulation setting
 - Graph type: Bipartite, Random DAG, Small-World, Scale-Free, Tree
 - 10 edges (6 continuous + 4 multinomial nodes)
 - 3 of continuous nodes are discretized as categorical variables. 
 - "mc" used the origianl data (sort of 'Oracle case'), "mm" used the discretized data.
 - 100 iterations
 - $\varepsilon=(0.05, 0.1, 0.2, 0.3, 0.4, 0.5)$
 - $\gamma=(0.05, 0.1, 0.2, 0.3, 0.4, 0.5, 1)$

2. SHD cases

```{r, echo=FALSE}
global_table = readRDS("global_table.rds")
global_modified <- global_table[global_table$method != "mo", ] 
p <- ggplot(global_modified, 
            aes(x = thre, y = SHD,  group = method, color = method))
p + geom_point() + geom_line() +  
  facet_grid(vars(graph), vars(lam_eps))
```

3. JI cases

```{r, echo=FALSE}
p <- ggplot(global_modified, 
            aes(x = thre, y = JI,  group = method, color = method))
p + geom_point() + geom_line() +  
  facet_grid(vars(graph), vars(lam_eps))
```

4. FDP cases

```{r, echo=FALSE}
p <- ggplot(global_modified, 
            aes(x = thre, y = FDP,  group = method, color = method))
p + geom_point() + geom_line() +  
  facet_grid(vars(graph), vars(lam_eps))
```

## What's next?
1. When $\gamma$ or $\varepsilon$ gets larger, SHD tends to decrease, but JI (Large is better) also decreases, too. JI seems to have its peak among the all the value of thresholds ($\gamma$).  
2. Need to find out the possible optimal point. 




